%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Paulo Gugelmo Cavalheiro Dias} \\[7.5pt]
\href{https://github.com/Paulogcd}{\raisebox{-0.05\height}\faGithub\ Paulogcd} \ $|$ \ 
\href{https://www.linkedin.com/in/paulo-gugelmo-cavalheiro-dias/}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ 
\href{https://paulogcd.com}{\raisebox{-0.05\height}\faGlobe \ paulogcd.com} \ $|$ \ 
\href{mailto:paulo.gugelmocavalheirodias@sciencespo.fr}{\raisebox{-0.05\height}\faEnvelope \ Email} \ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

\hfill \break

%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Global Impact Metrics - Economic Consultant} & \hfill November 2024 - Present \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item Quantitative analysis and management of large-scale datasets.
    \item Statistical analysis and reproducible research workflows.
    \item Literature reviews, evidence synthesis, and public policy analysis.
    \item Impact evaluation and cost-benefit analysis.
    \item Internal web services deployment management.
\end{itemize}
} \
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Marc Bloch Research Center} & \hfill April 2023 - August 2023 \\
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Research support and literature review.
        \item Academic event coordination and administrative support.
    \end{itemize}
} \\

\textbf{French-German Chamber of Commerce and Industry} & \hfill September 2022 - March 2023 \\
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Economic analysis of firms.
        \item Commercial data collection, management, and reporting.
    \end{itemize}
    } \\

\textbf{Beauchamp Town Hall} & \hfill July 2022 - September 2022 \\
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Economic and local public policy analysis.
        \item Data collection and statistical reporting.
    \end{itemize}
} \\

\textbf{Sciences Po, Centre de Sociologie des Organisations (CSO)} & \hfill July 2021 - September 2021 \\
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
        \item Data collection through the Twitter API using R.
        \item Data processing, management, and preparation for empirical analysis.
        \item Network visualisation with the igraph package. 
    \end{itemize}
} \
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	

2023 – 2025 & Master's of Research in Economics at \href{https://www.sciencespo.fr/en/}{Sciences Po}: \\
& \begin{itemize}
    \item Macroeconomics, Microeconomics, Econometrics - I, II, and III.
    \item Programming classes (Project management, R, Julia, Python).
    \item Financial Economics, Labor Economics, Public Economics.
    \item International Trade, Political, Organizational, and Development Economics.
\end{itemize}
My \href{https://www.paulogcd.com/Master_Thesis/}{Master's Thesis}, under the supervision of \href{https://www.jcommault.com}{Jeanne Commault}
and \href{https://www.paul-bouscasse.com}{Paul Bouscasse}, was one of the \href{https://www.sciencespo.fr/ecole-recherche/en/academics/masters/master-economics/best-thesis/}{"Best Master Thesis"} with a grade of 16.5/20 \\
\\
2019 – 2023 & Double Bachelor in Social Sciences and Political Science at \href{https://www.sciencespo.fr/en/}{Sciences Po} and \href{https://www.fu-berlin.de/en/index.html}{Freie Universität}\\

2019 – 2022 & Bachelor in Economics and Business at \href{https://www.univ-lorraine.fr/en/}{Lorraine University}\\

2019 & Baccalauréat at \href{https://www.lyc-polyvalent-monod-enghien.fr/}{Gustave Monod Highschool, Enghien-les-Bains} \hfill \\

2019 & Abitur at \href{https://www.lyc-polyvalent-monod-enghien.fr/}{Gustave Monod Highschool, Enghien-les-Bains} \hfill \\

\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
    Programming & \begin{itemize}
        \item R : Advanced level for data analysis, data management, economic modelling, package management.
        \begin{itemize}
            \item Statistical analysis (tydiverse packages: dplyr, tidyr, etc., data.table, igraph),
            \item Data collecting (rvest, httr),
            \item Data visualization (ggplot2, rmarkdown, Shiny), package management.
        \end{itemize}
        \item Julia : Advanced level for data analysis, data management, economic modelling, package management.
        \begin{itemize}
            \item Statistical Analysis (descriptive analysis, inferential statistics tools, GLM.jl, etc...),
            \item Economic modelling (macroeconomics models, simulations, numerical solving of analytically unsolvable equations),
            \item Numerical methods (parallel computing, value-function iteration, policy-function iteration, algorithmic assessment),
            \item Results presentation via integration to frameworks such as Plotly and Quarto.
        \end{itemize}
        \item Elementary level with other statistical softwares : Stata, MATLAB.
        \item Elementary level in Python, SQL, and C.
    \end{itemize} \\

    Web Development  &
    \begin{itemize}
        \item Web application services management and deployment with Docker.
        \item GitLab / GitHub CI/CD test and deployment.
        \item Experience with the Quarto framework (see my \href{https://www.paulogcd.com}{ main website}).
    \end{itemize} \\

    Others \quad \quad \quad \quad \quad \quad &
    \begin{itemize}
        \item Microsoft Office Suite.
        \item \LaTeX.
        \item Shell and Unix architecture knowledge, services management with systemctl.
        \item Experience in VPN deployment with Wireguard.
        \item Version control and code management with git.
    \end{itemize}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Selected Projects}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\href{https://www.paulogcd.com/Master_Thesis}{Master Thesis Website and Replication Package} &
Repository-based companion website for a computational Master's thesis, developed using Julia, Pluto.jl, Quarto, and Plotly.
Provides interactive visualizations, reproducible notebooks, and a complete replication package, illustrating modern workflows for computational and reproducible research. \\

\href{https://www.paulogcd.com/Replication_Monge_et_al_2019.jl/dev/}{Replication of Monge-Naranjo et al. (2019)} &
Group project involving the translation of the original Stata replication package of \textit{Natural Resources and Global Misallocation} (American Economic Journal: Macroeconomics, 2019) to Julia. Developed for Florian Oswald's Computational Economics course at Sciences Po. The project emphasizes reproducibility and demonstrates the use of Julia for computational economics. \\

\href{https://www.paulogcd.com/portfolio_tutorial/}{Research Portfolio Tutorial} &
Tutorial introducing the creation and maintenance of an online research portfolio using VS Code, Git, GitHub, Quarto, and GitHub Pages. Designed to help fellow research students develop reproducible workflows and communicate their work online. \\

\end{tabularx}


%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\section{Languages}
\begin{tabularx}{\linewidth}{@{}l X@{}}
French &  \normalsize{Native (C2)}\\
Portuguese &  \normalsize{Spoken (C2)}\\
German &  \normalsize{Professional level (C1)}\\  
English &  \normalsize{Professional level (C1) - TOEFL : 104/120}\\ 
Spanish & \normalsize{Beginner level (B1)}\\ 
Italian & \normalsize{Beginner level (B1)}\\ 
\end{tabularx}

\section{References}

\href{https://floswald.github.io}{Prof. Florian Oswald} - florian.oswald@gmail.com \\
\href{https://www.jcommault.com}{Prof. Jeanne Commault} - jeanne.commault@sciencespo.fr \\
\href{https://www.paul-bouscasse.com}{Prof. Paul Bouscasse} - paul.bouscasse@sciencespo.fr \\

\vfill
\center{\footnotesize Last updated: \today}

\end{document}